Image Processing for Discovering\\ the Rules of Video Games

### 2018-04-11 proposal/paper.tex

\section*{Image Capture}
An image capture script written in Lua was used to interface with our platform to capture frames from the game. The image capture takes screen shots of the game every 10 frames. Since the game is being run at about 60 frames per second, it captures 6 frames per second.

\section{Solution}

@@

@@

>>>>

\section{Image Capture}
An image capture script written in Lua was used to interface with our platform to capture frames from the game. The image capture takes screen shots of the game every 10 frames. Since the game is being run at about 60 frames per second, it captures 6 frames per second.

\section{Image Recognition}
With each image captured, the next algorithm is to convert each image using opencv so it can be read and encoded by the QLearning algorithm.

\section{QLearning}
QLearning is an algorithm that uses Model-Based Learning. It is an evolved form of Markov Chains. To summarize QLearning, it takes a state, and then has transitions from its current state into future states. Each transition has a probability of being taken to move into the next state. Each possible state that can be transitioned into (known as a future state) has a reward or penalty associated with it. QLearning will at first pick a future state at random, and then, based on whether a reward or penalty is reached, update the transition probability. What makes QLearning so appealing for learning games is that it can on occasion, take a route that seems sub-optimal to explore whether that future state (or any subsequent future state) might lead to greater rewards. This is good for games that have random chance outcomes that are sometimes bad, but sometimes good.

\section{Results}

@@

\section{Conclusion}

@@

\bibitem{4}
    S. Raval, "Q Learning Explained", December 1, 2017. Available: https://www.youtube.com/watch?v=aCEvtRtNO-M
